---
title: "Get started with bones"
output: rmarkdown::html_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment  = "#>",
  eval     = FALSE # Shiny apps can't run inside a static document.
)
```

A spinner tells the user to wait. A skeleton shows the user what is coming:
bars for a bar chart, rows for a table, lines for text. The page does not
look empty, and the eye of the user can go to the place where the content
will be.

## Install

`bones` is not on CRAN yet. Install it from GitHub:

```{r}
# install.packages("remotes")
remotes::install_github("tenmeh/bones")
```

## Wrap an output

Put `withBones()` around an output in the UI. That is all:

```{r}
library(shiny)
library(bones)

ui <- fluidPage(
  withBones(plotOutput("chart")),
  withBones(tableOutput("results"), rows = 8)
)
```

`bones` finds the shape from the output. A `plotOutput()` gets columns on
an axis, a `tableOutput()` gets a header row and body rows, and a
`textOutput()` gets lines of text. A table from DT, reactable, gt or
rhandsontable gets a shape that copies that package. The
[Shapes](shapes.html) page shows each one.

## Name the shape when bones cannot find it

A `plotOutput()` only says that a plot will be there. `renderPlot()`
decides the kind of chart later, on the server. So name the kind with
`type`:

```{r}
withBones(plotOutput("trend"), type = "line")
withBones(plotOutput("fit"),   type = "scatter")
```

A `uiOutput()` can hold anything, so give it a `type` too:

```{r}
withBones(uiOutput("kpis"),  type = "value", n = 3)
withBones(uiOutput("cards"), type = "cards", n = 4)
```

## The page does not move

Until the content arrives, the placeholder keeps the height of the output.
If the output sets a height, as `plotOutput()` does, the placeholder uses
it. If not, the height comes from `rows`, `lines` or `n`, or from `height`:

```{r}
withBones(uiOutput("summary"), type = "text", lines = 5)
withBones(uiOutput("map"),     type = "plot", height = 500)
```

When the content arrives, the content sets the height, and no gap stays
under it.

## The second load keeps the old content

On the first load, the user sees a skeleton. When the output calculates
again, the old content stays on the screen, dimmed, until the new content
arrives. The user is possibly in the middle of reading it, and grey boxes in
its place would remove information.

To show the skeleton again on each load, set `stale = FALSE`:

```{r}
withBones(plotOutput("chart"), stale = FALSE)
```

## Set the look for the whole app

`bones_defaults()` sets the animation, the colours and the speed for the
session. An argument to `withBones()` is stronger than a default:

```{r}
bones_defaults(
  animation = "pulse",   # "wave" (the default), "pulse" or "none"
  radius    = "0.5rem",
  speed     = 2,
  stale     = FALSE
)
```

The default colours come from the theme of the page: the text colour of
the bslib theme, made faint. A skeleton thus takes the tint of a branded
theme, and turns light in a dark theme, with no configuration. With no
Bootstrap 5 theme, the colours are neutral greys. Users who ask their system
to reduce motion get no animation.

## A placeholder with no output

`bones_skeleton()` makes a skeleton on its own, for a place where there is
no Shiny output:

```{r}
output$panel <- renderUI({
  if (is.null(data())) return(bones_skeleton("table", rows = 5))
  tableOutput("results")
})
```
