---
title: "Shapes"
output: rmarkdown::html_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", echo = FALSE)
library(bones)

# Each skeleton on this page is a real bones_skeleton(), not a picture. It
# moves with the "wave" animation, as it does in an app.
gallery <- function(types, height = 200, ...) {
  htmltools::div(
    style = paste(
      "display: grid; gap: 1.25rem; margin: 1rem 0 2rem;",
      "grid-template-columns: repeat(auto-fill, minmax(260px, 1fr));"
    ),
    lapply(types, function(type) {
      htmltools::div(
        htmltools::tags$code(sprintf('type = "%s"', type)),
        htmltools::div(
          style = "margin-top: 0.5rem;",
          bones_skeleton(type, height = height, ...)
        )
      )
    })
  )
}
```

Each skeleton below is drawn by `bones_skeleton()` on this page. In an app,
`withBones()` draws the same shape around an output.

## Text, cards and values

`textOutput()` and `uiOutput()` get the text shape. Use `"cards"` and
`"value"` for a `uiOutput()` that holds cards or value boxes.

```{r}
gallery(c("text", "cards", "value"), height = 140)
```

## Charts

A `plotOutput()` gets the bar shape. It cannot say what kind of chart it
will hold, because `renderPlot()` decides that later, on the server. So give
the kind with `type`: `withBones(plotOutput("p"), type = "scatter")`.

```{r}
gallery(c("plot", "bar", "line", "area", "scatter", "histogram", "pie", "heatmap"))
```

## Maps, networks, timelines and word clouds

These shapes are also for widgets. `bones` finds them from the output: a
`leaflet::leafletOutput()` gets the map, a `visNetwork::visNetworkOutput()`
gets the network, and so on. Give `type = "map"` to a map that draws into a
`plotOutput()`, such as one from ggmap.

```{r}
gallery(c("map", "network", "timeline", "wordcloud"))
```

## plotly, echarts4r and highcharter

A `plotly::plotlyOutput()`, `echarts4r::echarts4rOutput()` or
`highcharter::highchartOutput()` can hold any kind of chart, so its first
skeleton has the bar shape. When its first value arrives, `bones` reads the
kind of the chart from its series, and the next loads show that shape:
bar, line, area, scatter, histogram, pie, heatmap, map, network or word
cloud. A kind with no shape, such as a box plot, keeps the bar shape. `bones` stores the
kind in the browser too, so on the next visit the first skeleton has the
right shape. Set `remember = FALSE` to store nothing, or give `type` to
choose the shape yourself.

## Tables

A `tableOutput()` gets the plain table shape. A table from a table package
gets a shape that copies that package, and `bones` finds the package from
the output, with no `type`. Set `rows` to the number of rows on a page.

```{r}
gallery(c("table", "dt", "reactable", "gt", "rhandsontable"), height = NULL, rows = 5, cols = 4)
```
